%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[nofonts, letterpaper]{tufte-handout}

%\geometry{showframe} % display margins for debugging page layout

\usepackage{graphicx} % allow embedded images
  \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
  \graphicspath{{img/}} % set of paths to search for images
  
\usepackage{fontspec}
  \setmainfont[Ligatures={Common,TeX},Numbers={Proportional}]{Linux Libertine O}
  \setsansfont{Linux Biolinum O}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{multicol} % multiple column layout facilities
%\usepackage{hyperref}
%\usepackage{fancyvrb} % extended verbatim environments
%  \fvset{fontsize=\normalsize}% default font size for fancy-verbatim environments

% Change the header to shift the title to the left side of the page. 
% Replaced \quad with \hfill.  See \plaintitle in tufte-common.def
{\fancyhead[RE,RO]{\scshape{\newlinetospace{\plaintitle}}\hfill\thepage}}

\makeatletter
% Paragraph indentation and separation for normal text
\renewcommand{\@tufte@reset@par}{%
  \setlength{\RaggedRightParindent}{1.0pc}%
  \setlength{\JustifyingParindent}{1.0pc}%
  \setlength{\parindent}{1pc}%
  \setlength{\parskip}{0pt}%
}
\@tufte@reset@par

% Paragraph indentation and separation for marginal text
\renewcommand{\@tufte@margin@par}{%
  \setlength{\RaggedRightParindent}{0pt}%
  \setlength{\JustifyingParindent}{0.5pc}%
  \setlength{\parindent}{0.5pc}%
  \setlength{\parskip}{0pt}%
}

\makeatother

\title{Study Guide 09}
\author{Rocky and Kelp Communities}

\date{} % without \date command, current date is supplied

\begin{document}

\maketitle	% this prints the handout title, author, and date

%\printclassoptions

\section{Vocabulary}
\marginnote{\textbf{Study:} pgs. 418--432.}
\vspace{-1\baselineskip}
\begin{multicols}{2}
subtidal \\
sublittoral \\
infralittoral \\
circalittoral \\
keystone species \\
trophic cascade \\
alternate stable states
\end{multicols}

\section{Concepts}

\begin{enumerate}
\item
  Discuss how the abiotic environmental parameters found in the
  sublittoral zone affect community structure. Be sure to account for
  depth gradients. Where do the abiotic factors have the greatest
  influence on community structure, and why?
\item
  Discuss the biotic factors that affect sublittoral community
  structure. How does this interact with each other to influence
  structure?
\item
  What is the infralittoral zone? What is the circalittoral zone? Does
  the bottom of the infralittoral zone always coincide with the maximum
  depth range at which kelp can grow? Why or why not?
\item
  What are two keystone species that affect community structure near the
  bottom of the kelp zone? Explain how these species influence diversity
  in the sublittoral.
\item
  Describe the long-term interactions between kelp and sea urchins and associated alternate stable states.
  How do you think this would influence patch dynamics and diversity at
  larger scales (say, along the western coast of Washington, Oregon,
  California and Baja California?)
\item
  What is a trophic cascade? Describe a trophic cascade that is
  representative of rocky subtidal communities.
 \end{enumerate}


\end{document}