\textbf{Terms: Know definitions, how they relate to concepts, recognize
them based on concepts.}

zooxanthellae

reef flat

reef crest

fore-reef slope

interference competition

exploitative competition

\textbf{Concepts: remember you may have to synthesize individual
concepts within a lecture or across lectures. Think broadly.}

\begin{itemize}
\item
  Coral reefs are biogenic ecosystems. What is a biogenic ecosystem?
  What other ecosystems did we study that are biogenic?
\item
  List the major physical factors that determine the global distribution
  of coral reefs (not zonation within reefs)? Relate each factor to the
  biology of corals to explain the distributional pattern.
\item
  What are the sources of GPP on coral reefs? If reefs are so highly
  productive, why does the water around the reefs not show signs of
  higher NPP exported from the reef? If the waters are nutrient-poor,
  what are the nutrient sources for reef GPP?
\item
  Why is coral reef diversity (not just corals themselves) highest in
  the Indo-West Pacific, particularly around Indonesia? Why is coral
  reef diversity lower in the Caribbean Sea? Offer both evolutionary and
  ecological explanations.
\item
  Draw a profile of a typical coral reef and label the zones. Explain
  the physical and biological factors that determine zonation on a coral
  reef. Which factors, physical or biological, best explain the pattern
  of zonation? Why?
\item
  For each zone, state whether competition, predation and
  positive-species interactions (e.g., mutualism) are high, moderate or
  low. Explain why for each.
\item
  Explain the difference between interference and exploitative
  competition. Which types of corals tend to show exploitative
  competition? Which types of corals tend to show interference
  competition? How is the balance between these two groups of species
  affected by corallivorous fishes?
\item
  Explain why coral reefs show enormous variation in community structure
  and assemblage in both space and time?
\item
  Explain the four hypotheses that have been proposed to explain the
  community structure of fishes on coral reefs.
\end{itemize}
