%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[12pt, addpoints]{exam}

%\printanswers

\usepackage{fontspec}
\setmainfont[Ligatures={Common,TeX}, BoldFont={* Bold}, ItalicFont={* Italic}, BoldItalicFont={* BoldItalic}, Numbers={OldStyle}]{Linux Libertine O}
\setsansfont[Scale=MatchLowercase,Ligatures=TeX, Numbers=OldStyle]{Linux Biolinum O}
\usepackage{microtype}


\usepackage{geometry}
\geometry{letterpaper, bottom=1in}                   
\usepackage[parfill]{parskip} 

% This defines \amper for the fancy ampersand
% to be used in the header. See
% https://tex.stackexchange.com/a/58185/39194
\usepackage{xspace}
\newfontfamily\amperfont[Style=Alternate]{Linux Libertine O}    
\makeatletter
\DeclareRobustCommand{\amper}{{\amperfont\ifx\f@shape\scname\smaller[1.2]\fi\&}\xspace}
\makeatother


\usepackage{hanging}

\usepackage[sc]{titlesec}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\usepackage{enumitem}
\setlist{leftmargin=*}
\setlist[1]{labelindent=\parindent}
\setlist[enumerate]{label=\textsc{\alph*}.}
\setlist[itemize]{label=\color{gray}\textbullet}
\usepackage{hyperref}

\renewcommand{\questionshook}{%
	\setlength{\leftmargin}{-\leftskip}%
}

\renewcommand{\solutiontitle}{\noindent}
\unframedsolutions
\SolutionEmphasis{\bfseries}

\pagestyle{headandfoot}
\firstpageheader{\textsc{bi} 434: Marine Ecology \amper Conservation}{}{\ifprintanswers\textbf{KEY}\else Critical Analysis\fi}
\runningheader{}{}{\footnotesize{pg. \thepage}}
\footer{}{}{}
\runningheadrule

\newcommand*\AnswerBox[2]{%
    \parbox[t][#1]{0.92\textwidth}{%
    \begin{solution}#2\end{solution}}
%    \vspace*{\stretch{1}}
}

\newenvironment{AnswerPage}[1]
    {\begin{minipage}[t][#1]{0.92\textwidth}%
    \begin{solution}}
    {\end{solution}\end{minipage}
    \vspace*{\stretch{1}}}

\newlength{\basespace}
\setlength{\basespace}{5\baselineskip}

\begin{document}

\subsection*{Sea-Level Rise (\numpoints\ points)}

Read carefully the paper listed below and then type your answers to the 
following questions. Type the question number and then your answer. You 
do not need to retype the question. You must submit your answers before 
class starts or your assignment will be considered late. 

These questions focus on the components of sea-level rise. You should at
least skim the rest of the paper but read it at some point to be a 
better informed scientist and global citizen.

\textbf{Failure to attend} \textbf{class} \textbf{on the due date} will
result in an automatic 50\% deduction.

\begin{hangparas}{1.5em}{1}
Durand, G., M.\,R.\ van den Broeke, G.\ Le Cozannet, T.\,L.\ Edwards, P.\,R.\ Holland, N.\,C.\ Jourdain, B.\ Marzeion, R.\ Mottram, R.\,J.\ Nicholls, F.\ Pattyn, F.\ Paul, A.\,B.\,A.\ Slangen, R.\ Winkelmann, C.\ Burgard, C.\,J.\ van Calcar, J.-B.\ Barré, A.\ Bataille, and A.\ Chapuis.
2022. Sea-level rise: from global perspectives to local services. Frontiers in Marine Science 8, Article 709595. doi: 10.3389/fmars.2021.709595 
\end{hangparas}


\begin{questions}
\question[5]
Explain what is thermal expansion and how it contributes to sea level 
rise. What would be the \emph{average} projected sea level rise by 2100 
due to thermal expansion? Use the best and worst case \textsc{ssp} 
scenarios to make your calculation.


\ifprintanswers\textbf{%
As water warms, it's volume increases or expands. This causes sea level 
to rise farther inshore. Best case scenario is 0.12 m and worst case
scenario is 0.3 m, so average is 0.21 m.
}\fi

\question[10]
Describe marine ice sheet instability in your own words. What is the 
importance of the grounding line? How is \textsc{misi} contributing
to acceleration of glaciers in Amundsen Sea Embayment? \textsc{Side bar:}
Two important glaciers in Amundsen Sea contributing to sea-level rise
are Pine Island and Thwaites. Thwaites Glacier alone is estimated to
contain about 65 cm (2 feet) of sea level rise that could happen in
within a couple decades. If Thwaites collapses entirely, that could
unleash 10 feet or more of sea level rise over 1–2 centuries. For this
reason, Thwaites is sometimes called the Doomsday Glacier (cue dramatic 
music). Wikipedia has a brief, helpful video on 


\ifprintanswers\textbf{%
As the glacier leaves land, it becomes a floating ice sheet. The 
grounding line is where the glacier makes contact with land. It is
the weight of the ice that keeps it in contact with the ground. As the 
glacier thins, the weight is insufficient to keep the glacier in contact 
with the ground. More water gets underneath, thinning the sheet further,
creating a feedback loop. In Amundsen, the grounding line is on a 
negative slope (gets farther below sea level as you go inland) so more 
water can get underneath, and floating the thicker ice sheet. This 
speeds up the rate of advance.
}\fi

\question[5]
Ice mass balance is the difference between ice gain through snowfall and 
ice loss through melting and calving of glaciers to form icebergs. 
Describe how Greenland's ice mass balance is changing due to 
melt-elevation feedback and melt-albedo feedback. Be sure to explain
the meaning of these two terms.

\ifprintanswers\textbf{%
Lower elevations are warmer, so as the glacier melts and becomes 
thinner, the surface is at lower, warmer elevation, thus melting even
more. The melting ice surface also becomes darker, so it absorbs more
heat instead of reflecting it (melt-albedo). Thus, a positive feedback
loop is created. As glaciers melt, they get warmer, and thus melt more, 
etc.
}\fi


\question[5]
Cold, dense surface water of the Atlantic Meridional Overturning 
Circulation system (\textsc{amoc, aka} Great Ocean Conveyor) sinks at 
two locations east and west of southern Greenland, and at a third 
location in the Weddell Sea of Antarctica. Predict how melting runoff 
from Greenland and Antarctica might affect the rate of circulation of 
the \textsc{amoc.}
 
\ifprintanswers\textbf{%
Freshwater input will decrease salinity of the surface water, decreasing
density and thus making it harder for the surface water to sink. This
should slow the rate of circulation.
}\fi

\ifprintanswers
Interactive sea level rise viewer.

\url{https://coast.noaa.gov/slr/}
\fi
\end{questions}


\end{document}  