%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, twoside]{article}

% FONTS
\usepackage{fontspec}
\def\mainfont{Linux Libertine O}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setmainfont[Ligatures={Common}, Contextuals={NoAlternate}, BoldFont={* Bold}, ItalicFont={* Italic}, Numbers={OldStyle}]{\mainfont}
\setmonofont[Scale=MatchLowercase]{Linux Libertine Mono O} 
\setsansfont[Scale=MatchLowercase]{Linux Biolinum O} 
\usepackage{microtype}

% This defines \amper for the fancy ampersand
% to be used in the header. See
% https://tex.stackexchange.com/a/58185/39194
\usepackage{xspace}
\newfontfamily\amperfont[Style=Alternate]{Linux Libertine O}    
\makeatletter
\DeclareRobustCommand{\amper}{{\amperfont\ifx\f@shape\scname\smaller[1.2]\fi\&}\xspace}
\makeatother

\usepackage[left=0.75in,right=0.75in,top=0.8in,bottom=0.9in]{geometry} 
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\usepackage[singlelinecheck=false]{caption}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{enumitem}

\newlength{\mylength}
\settowidth{\mylength}{\small{7.}}

\begin{document}
\begin{landscape}
{\small%
\begin{longtable}[l]{@{}L{5cm}L{3.5cm}L{3.5cm}L{3.5cm}L{3.5cm}L{1.9cm}@{}}
\caption*{\textsc{bi} 634: Grading rubric for conservation plan presentation. 50 points.}\\
\toprule
Content Areas & Unsatisfactory (0 points) & Borderline (10 points) & Satisfactory (15 points) & Outstanding (20 points) & Score \\ 
\midrule
\endfirsthead
\toprule
Content Areas & Unsatisfactory (0 points) & Borderline (4 points) & Satisfactory (7 points) & Outstanding (10 points) & Score\\ 
\midrule
\endhead
%% Row 1
\textbf{Conservation plan:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item Title and list of team members,
\item Habitat or ecosystem,
\item Ecosystem services,
\item Need for conservation or restoration,
\item Summary of each objective,
\item Public awareness plans,
\item Long term monitoring,
\item Total budget and time frame.
\end{enumerate}&%
Covered $\leq$ 3 of the content areas in depth and the others either not at all or briefly. &%
Covered 4--6 of the content areas in depth and the others either not at all or briefly. &%
Covered 7--8 of the content areas in depth and the others either not at all or briefly. &%
Covered all content areas in depth.&%
\\[-1em]
\midrule
	 & Unsatisfactory (0 points) & Borderline (4 points) & Satisfactory (7 points) & Outstanding (10 points) & Score \\ 
\midrule
%% Row 2
\textbf{Quality of slides:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item $\leq$ 6 Sentences per slide and $\leq$ 6 words per sentence, not including citations, %
\item Citation included,\footnote{Citations should refer to Literature Cited in conservation plan. Do not include a Literature Cited as part of your presentation.} \par%
\item No spelling or grammatical errors,\par%
\item Figures / tables were legible.\end{enumerate}&%
Met none of the content areas. &%
Met 1--2 of the content areas. &%
Met 3 of the content areas. &%
Met all 4 of the content areas.&%
\\[-1em]
\midrule
%% Row 3
\textbf{Delivery pace and style:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item Presentation lasted 15 minutes leaving 5 minutes for questions, \par%
\item Student’s voice was clear, \par%
\item Student had correct, precise pronunciation of terms,\par%
\item Student used slides as a guide: added more information than on slides.\end{enumerate}&%
Met none of the content areas. &%
Met 1--2 of the content areas. &%
Met 3 of the content areas. &%
Met all 4 of the content areas.&%
\\[-1em]
\midrule
%% Row 4
\textbf{Response to questions:}\par%
\vspace{-0.5\baselineskip}
\begin{enumerate}[itemsep=-0.25\baselineskip,align=left, leftmargin=*]
\item Student was able to answer questions with depth and clarity.\end{enumerate}&%
Did not answer any of the questions. &%
Answered all questions but without any depth and clarity \emph{or} answered less than half with depth and clarity. &%
Answered most questions with depth and clarity. &%
Answered all questions with depth and clarity.&%
\\
\midrule
& & & & \vspace{0.5in}\par\hfill\normalsize{Total Score\phantom{m}} & \\
\bottomrule
\end{longtable}
}%End small font size

\end{landscape}
\end{document}